The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-10 papers/pair-correlation/paper.tex
More plot tweaks. All plots now use latex fonts, and all garbage mc data is gone. Tested on paho-arch. Took 0:49.16.

\newcommand\paircaption{\pahosays{The MC has one point that jumps up at the
    beginning of the incontact region.} The pair distribution function near a
  hard wall, with packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with
  the hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$ as $\rr_2$
  varies.  The top half of this figure shows the result of the Monte Carlo
  simulation, while the bottom half shows the result of the appproximation
  developed in this work.  On the right is a plot of $g^{(2)}(\rr_1,\rr_2)$ on
  the path illustrated in the figure to the left.  This plot compares the Monte
  Carlo results (black) with those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at contact, where
  it is defined.  }

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for this
      work}\fixme{Fix MC issue here (volume wrong?)} \fixme{Add backward curve
      for this work mc?}The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when $\rr_1$
    and $\rr_2$ are in contact.  The color plot on the left shows the triplet
    distribution function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows the value of
    $g^{(3)}$ along the path shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}

>>>>

\newcommand\paircaption{The pair distribution function near a hard wall, with
  packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with the hard wall.
  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$ as $\rr_2$ varies.  The top
  half of this figure shows the result of the Monte Carlo simulation, while the
  bottom half shows the result of the appproximation developed in this work.  On
  the right is a plot of $g^{(2)}(\rr_1,\rr_2)$ on the path illustrated in the
  figure to the left.  This plot compares the Monte Carlo results (black) with
  those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at contact, where
  it is defined.  }

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Make note of the double curves}\fixme{Add backward curve for
      this work mc?}\pahosays{would annotations be clearer if they were on the
      x/z ticks instead of arrows?}The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when $\rr_1$
    and $\rr_2$ are in contact.  The color plot on the left shows the triplet
    distribution function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows the value of
    $g^{(3)}$ along the path shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}
